Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-14 paper.tex
First draft of conclusion

\xcom{Do we want to add potential improvements? Like an index closer to the naive algorithm.}

TODO

>>>>

We have presented a technique that integrates forward reasoning into a tree-based proof search procedure supporting arbitrary proof rules.
We avoid redundant reasoning steps by caching partial forward rule applications in a data structure, the \emph{forward match state}, that enables efficient updates.
The technique is independent of the search strategy and logic used.
Our evaluation shows a substantial speedup on some synthetic benchmarks, relative to Aesop's previous implementation.
